Extracting Angular Observables without a Likelihood\\and Applications to Rare Decays

### 2015-01-22 draft.tex
[draft] Rewrite abstract

\begin{abstract}
In this letter we study how to obtain a set of angular observables
$\{S_i\}$ that arise in a generic multi-body process without the need
to carry out a likelihood fit of an angular distribution to the
measured events. Instead, we present a method that only relies on
orthogonality of angular functions, and estimation of integrals
by means of Monte Carlo techniques. Beyond providing estimators
for central values and uncertainties, we provide means to determine
the correlation between all angular observables. We show that detector
acceptance effects can be accounted for in the analysis.
\end{abstract}

>>>>

\begin{abstract}
  \fred{Our goal is to obtain a complete set} of angular observables
  arising in a generic multi-body process without the need to carry
  out a likelihood fit of the angular distribution to the measured
  events. Instead, we \fred{apply the method of moments} that relies
  both on the orthogonality of angular functions and the estimation of
  integrals by Monte Carlo techniques. \fred{The main advantage of
    this method is that the joint distribution of all observables
    given the data can be easily extracted, even for very few
    events. Our main contribution is to show explicitly how systematic
    uncertainties from detector-resolution and acceptance effects can
    be incorporated in a general algorithm. Finally, we present the
    necessary process-dependent formulae needed for direct
    implementation of the method for several rare decays currently of
    interest.}
\end{abstract}
